Stability and Performance of Coalitions of Prosumers Through Diversification in the Smart Grid

### 2015-11-23 Article.tex
authors update

\begin{document}
\pagestyle{plain}
\pagenumbering{arabic}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Authors
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author{Nicolas Gensollen, Vincent Gauthier, Monique Becker and Michel Marot \\
\IEEEauthorblockA{CNRS UMR 5157 SAMOVAR, \\
Telecom SudParis/Institut Mines Telecom\\
Email: \{nicolas.gensollen, vincent.gauthier, michel.marot, monique.becker\}@telecom-sudparis.eu}}

@@

\begin{figure}
\label{fig:process}
	\includegraphics[scale=.45]{Fig2}
	\caption{Process}
\end{figure}

>>>>

\begin{document}
%\pagestyle{plain}
%\pagenumbering{arabic}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Authors
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author{Nicolas Gensollen, Vincent Gauthier, Monique Becker and Michel Marot
%\IEEEauthorblockA{CNRS UMR 5157 SAMOVAR, \\
%Telecom SudParis/Institut Mines Telecom\\
%Email: \{nicolas.gensollen, vincent.gauthier, michel.marot, monique.becker\}@telecom-sudparis.eu}}
\thanks{Authors are with CNRS UMR 5157 SAMOVAR, Telecom SudParis/Institut Mines Telecom, e-mail: (\{nicolas.gensollen, vincent.gauthier, michel.marot, monique.becker\}@telecom-sudparis.eu)}}%

@@

\begin{figure}
	\includegraphics[scale=.45]{Fig2}
	\caption{Process}
\label{fig:process}
\end{figure}
